getwd()

setwd("/Users/ajdonna/Desktop/CoursesNpractice/FaceBook\ Data/")

```{r}
FB <- read.csv('FBposts.csv')

names(FB)
str(FB)

#COnverting YEAR into a FACTOR variable
FB$YEAR <- factor(FB$YEAR)

table(FB$YEAR)
```

#Getting the summary of Likes
```{r}
summary(FB$LIKES)
library(ggplot2)
ggplot(data=subset(FB, FB$YEAR!='2010'),aes(fYear, LIKES))+
  geom_boxplot()+
  ylim(0,50)
```
Notes: It is hard to foresee any trend in here. There was a increasing trend from 2013 to 2015 for the count in #Likes. But for years 2016 and 2017, the median LIKES for the posts are low as compared to previous years but the #POSTS depicting HIGH LIKE_COunt are more!


#Analyzing the LIKES of the POSTS
```{r}
library(ggplot2)
ggplot(data=FB,aes(LIKES))+
  geom_histogram(binwidth = 5,color='black',fill='#45AB6E')+
  geom_freqpoly()+
  scale_x_continuous(breaks = seq(0,250,25))
```

#Better view of LIKES by adjusting the binwidth
```{r}
ggplot(data=FB,aes(LIKES))+
  geom_histogram(binwidth = 25,color='black',fill='#45AB6E')+
  geom_freqpoly()+
  scale_x_continuous(breaks = seq(0,250,25))
```

#Let's see the similar PLOTS for comments
```{r}
summary(FB$COMMENTS)

ggplot(data = subset(FB, !is.na(COMMENTS)),aes(YEAR, COMMENTS))+
  geom_boxplot()
```
Notes: There are too many outliers outside of the INTER-QUARTILE range. Let's get a clearer picture for the same.

```{r}
ggplot(data = subset(FB, !is.na(COMMENTS)),aes(YEAR, COMMENTS))+
  geom_boxplot()+
  ylim(0,10)
```

Notes: It is surprising to see that for all the years, the 3rd quartile reaches only to 5 comments!Also, the median comments for most of the years have been 0, despite being too many outliers probably because of too many 0 values! We are not excluding the 0 values as they are the part of the data indicating that not too many comments are done on the posts as compared to LIKES!

#Summary of COmments by YEAR
```{r}
by(FB$COMMENTS, FB$YEAR, summary)
```

#Calculating the LIKES, COMMENTS, POSTS grouped by YEAR
```{r}
library(dplyr)
FB_YEAR <- subset(FB,!is.na(COMMENTS) & YEAR!='2010') %>%
  group_by(YEAR) %>%
  summarise(Mean_Likes = round(mean(LIKES)),
            Median_Likes = median(LIKES),
            Mean_Comments = round(mean(COMMENTS)),
            Median_Comments = median(COMMENTS),
            Likes=sum(LIKES),
            Comments=sum(COMMENTS),
            Posts = n())%>%
  arrange(YEAR)

write.csv(FB_YEAR, file='Yearly_FB_data.csv',row.names = FALSE)
```


#Finding the Yearly Distribution of POSTS by TYPE in LONG Format
```{r}
FB_TYPE_LONG <- subset(FB, !is.na(COMMENTS) & TYPE!='note' & YEAR != '2010')%>%
  group_by(YEAR,TYPE) %>%
  summarise(Posts = n(na.action()))%>%
  arrange(YEAR)
```


#Converting from LONG format to WIDE format
```{r}
library(reshape2)
FB_TYPE_WIDE <- dcast(FB_TYPE_LONG,
                      YEAR ~ TYPE,
                      value.var='Posts')
```


#Replacing the NA values in WIDE format with 0
```{r}
FB_TYPE_WIDE[is.na(FB_TYPE_WIDE)] <- 0
``` 

#Combining the COLUMNS from FB_TYPE_WIDE to FB_YEAR
```{r}
FB_YEAR$TYPE_LINK <- FB_TYPE_WIDE$link
FB_YEAR$TYPE_PHOTO <- FB_TYPE_WIDE$photo
FB_YEAR$TYPE_STATUS <- FB_TYPE_WIDE$status
FB_YEAR$TYPE_VIDEO <- FB_TYPE_WIDE$video

#Writing the DATAframe to a CSV file
write.csv(FB_YEAR, file='Yearly_FB_data.csv',row.names = FALSE)
```



##Calculating the LIKES, COMMENTS, POSTS grouped by YEAR, MONTH
```{r}
FB_MONTH <- subset(FB,!is.na(COMMENTS) & YEAR!='2010') %>%
  group_by(YEAR,MONTH) %>%
  summarise(Mean_Likes = round(mean(LIKES)),
            Median_Likes = round(median(LIKES)),
            Mean_Comments = round(mean(COMMENTS)),
            Median_Comments = round(median(COMMENTS)),
            Likes=sum(LIKES),
            Comments=sum(COMMENTS),
            Posts = n())%>%
  arrange(YEAR)
```


#Finding the Monthly Distribution of POSTS by TYPE in LONG Format
```{r}
FB_TYPE_MON <- subset(FB, !is.na(COMMENTS) & TYPE!='note' & YEAR != '2010')%>%
  group_by(YEAR,MONTH,TYPE) %>%
  summarise(Posts = n())%>%
  arrange(YEAR)
```

#Converting from LONG format to WIDE format
```{r}
FB_MON_TYPE <- dcast(FB_TYPE_MON,
                     YEAR + MONTH ~ TYPE,
                     value.var = 'Posts')
```

#Replacing the NA values in WIDE format with 0
```{r}
FB_MON_TYPE[is.na(FB_MON_TYPE)] <- 0
```

#Combining the COLUMNS from FB_TYPE_WIDE to FB_YEAR
```{r}
FB_MONTH$TYPE_LINK <- FB_MON_TYPE$link
FB_MONTH$TYPE_PHOTO <- FB_MON_TYPE$photo
FB_MONTH$TYPE_STATUS <- FB_MON_TYPE$status
FB_MONTH$TYPE_VIDEO <- FB_MON_TYPE$video

#Writing the DATAframe to a CSV file
write.csv(FB_MONTH, file='Monthly_FB_data.csv',row.names = FALSE)
```







